---
title: "Brisby Animals"
author: "A Allan"
date: "`r format(Sys.time(), '%d %B %Y')`"
output:
  word_document:
    reference_docx: ./reference/word_style_template.docx
  html_document:
    df_print: paged
---

# Background  
For funsies, let's explore the Animal Registration data from Brisbane City Council.

Data               | Details                       |  Other deets
-------------------|-------------------------------|-------------
BCC Animal permits | dl from https://www.data.brisbane.qld.gov.au/data/dataset/current-animal-related-permits | 2018-10-11               
  
##### - 
# Data tidying   
This data is very tidy to begin with, so not much tidying to be done.

```{r eval = TRUE, echo = TRUE}

# 1. Data tidying
source("scripts/1_tidy.R")

```

##### -
# Explore your data  
Want to explore:  
- Breed proportions
- Locations of breeds


```{r eval = TRUE}

# Script for X
source("scripts/2_explore.R")

```

##### - 
# Produce outputs  
In this section are scripts for producing final output from the data.  

```{r eval = FALSE}

# Reporting script
source(".reference/1_XXXXXX.Rmd")


```



##### - 
# Final notes  

Any other junk you need to add goes here!

