---
title: "Title goes here"
author: "A Allan"
date: "`r format(Sys.time(), '%d %B %Y')`"
output:
  word_document:
    reference_docx: ./reference/word_style_template.docx
  html_document:
    df_print: paged
---

# Background  
Basic description of the project.   
Also include a table of the data files that occur in this project and describe the location of a data dictionary.

Data        | Details                       |  Other deets
------------|-------------------------------|-------------
Data 1      | Description                   |  Total mess
Data 2      | etc...                        |  Hopefully less messy.   
  

##### - 
# Data tidying   
In this section are scripts for tidying your data.  

```{r eval = FALSE}

# 1. Does X.
source(".scripts/1_XXXXXX.R")

# 2. Does Y.
source(".scripts/2_XXXXXX.R")


```

##### -
# Explore your data  
In this section are scripts for exploring your data.  

```{r eval = FALSE}

# Script for X
source(".scripts/1_XXXXXX.R")

```

##### - 
# Produce outputs  
In this section are scripts for producing final output from the data.  

```{r eval = FALSE}

# Reporting script
source(".reference/1_XXXXXX.Rmd")


```



##### - 
# Final notes  

Any other junk you need to add goes here!

